\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-24 journalWallFriction/theory2robAlgs.tex
Retried in writing the delta configuration procedure.

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
\textcolor{red}{Shiva, this image is nice.  A few suggestions: ?TODO: Label the middle image 'Translate workspace around (0,0)', and draw the workspace outlines with different colors and thicknesses}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-move reachable sets are drawn in transparent blue.
}
\end{figure}

>>>>

% \textcolor{red}{[INSERT ONE IMAGE OF A 4-sided irregular convex polygon]}\\
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{irregular.pdf}\end{overpic}
\caption{\label{fig:irregular}
%\textcolor{red}{Shiva, this image is nice.  A few suggestions: ?TODO: Label the middle image 'Translate workspace around (0,0)', and draw the workspace outlines with different colors and thicknesses}
Workspace and $\Delta$ configuration space is shown for an arbitrary convex polygon with $n=4$ sides. The 2-move reachable sets are drawn in transparent blue.
}
\end{figure}
